Type cones of $\b{g}$-vector fans

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
associahedron

% marginal comments
\usepackage{todonotes}
\newcommand{\arnau}[1]{\todo[color=orange!30]{#1 --- A.}}
\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pg}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

@@

% PG et Yann
\newcommand{\field}{\mathbb{K}}
\newcommand{\cat}{\mathcal{C}}
\newcommand{\Hom}[1]{\operatorname{Hom}_{#1}}
\newcommand{\susp}{\Sigma}
\newcommand{\add}{\operatorname{add}}
\newcommand{\MOD}{\operatorname{mod}}
\newcommand{\End}[1]{\operatorname{End}_{#1}}
\newcommand{\spl}{\operatorname{sp}}
\newcommand{\Ksp}{K_0^{\spl}}
\newcommand{\Kg}{K_0^{\b{g}}}
\newcommand{\ind}{\operatorname{ind}}
\newcommand{\coker}{\operatorname{coker}}
\newcommand{\CC}{\phi}

@@

\begin{proposition}
\label{prop:alternativePolytopalRealization}
The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
\[
P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}
\]
to the polytope
\[
Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}.
\]
\end{proposition}

@@

@@

Introduction on the associahedron. Loday's associahedron. \\
Three proofs that the type cone of Loday's associahedron~\cite{Loday} is simplicial and therefore explicit description of all realizations as follows:...\\
Explain the parallel with $\b{g}$-vectors, $\b{c}$-vectors, etc.
\vincent{TODO}

@@

A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\bar Q\blossom$), and \defn{bending} otherwise.
We denote by~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) the multisets of vertices of peaks (resp.~deeps) of~$\omega$.

@@

@@

Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\walks|-|Q_0|$ extremal exchangeable pairs. Since this~$|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
\end{proof}

Combining \cref{coro:simplicialTypeCone}, \cref{prop:bijectionStringsWalks} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan.

\begin{corollary}
For any gentle quiver~$\quiver$ with no self-kissing walk and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \bigset{\b{z} \in \R^{\walks}}{\b{z} \ge 0 \text{ and } \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \ell_\sigma \text{ for all } \sigma \in \strings}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{corollary}

\begin{proof}
\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\walks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial. We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
\end{proof}

@@

\begin{remark}
\label{rem:meshARquiver}
Although not needed in the proof of \cref{prop:extremalExchangeablePairsNKC}, we note that the extremal exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ and their linear dependences~${\gvector{\cc{\sigma}} + \gvector{\hh{\sigma}} - \gvector{\hc{\sigma}} - \gvector{\ch{\sigma}}}$ precisely correspond to the meshes of the Auslander-Reiten quiver of~$\quiver$.
\end{remark}

@@

We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
It seems that two exchangeable walks are always kissing along a single distinguishable string.
We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know there distinguished substring).
Note however that
\begin{enumerate}
\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
\end{enumerate}

@@

\para{Nested complex}
%
Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a non-empty connected induced subgraph of~$\graphG$.
The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$, and all other tubes are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.

@@

We start with the case of the path.
Recall that the tubes of the path are the intervals of~$[n]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

\begin{proposition}
\label{prop:extremalExchangeablePairsA}
%The extremal exchangeable pairs for the nested fan of the path are precisely the pairs of intervals~$\{[i,j], [i+1,j+1]\}$ for~$1 \le i \le j \le n-1$.
Two intervals~$[i,j]$ and~$[i',j']$ of~$[n]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
\end{proposition}

>>>>

% marginal comments
\usepackage{todonotes}
\newcommand{\arnau}[1]{\todo[color=orange!30]{#1 --- A.}}
\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

@@

@@

\begin{proposition}
\label{prop:alternativePolytopalRealization}
\vincent{See \cite[Coro.~9.5.7]{DeLoeraRambauSantos}}
The affine map~$\Psi: \R^n \to \R^N$ defined by~$\Psi(\b{x}) = \b{h} - G\b{x}$ sends the polytope
\[
P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}
\]
to the polytope
\[
Q_\b{h} \eqdef \set{\b{z} \in \R^N}{\b{K}\b{z} = \b{K}\b{h} \text{ and } \b{z} \ge 0}.
\]
\end{proposition}

@@

\subsection{Faces of the type cone and Minkowski sums}

\begin{lemma}
\label{lem:MinkowskiSum}
For~$\b{h}, \b{h}' \! \in \R^N$, the polytope~$P_{\b{h} + \b{h'}}$ is the Minkowski sum of the polytopes~$P_\b{h}$~and~$P_{\b{h}'}$.
\end{lemma}

\begin{proof}
This follows from the definition of~$P_\b{h}$ and of Minkowski sums:
\begin{align*}
P_\b{h} + P_{\b{h}'} & = \set{\b{x} + \b{x}'}{\b{x} \in P_\b{h} \text{ and } \b{x}' \in P_{\b{h}'}} = \set{\b{x} + \b{x}'}{\b{G}\b{x} \le \b{h} \text{ and } \b{G}\b{x}' \le \b{h}'} \\
& = \set{\b{y} \in \R^n}{\b{G}\b{y} \le \b{h} + \b{h}'} = P_{\b{h} + \b{h}'}.
\qedhere
\end{align*}
\end{proof}

\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes. This provides natural Minkowski summands for all polytopal realizations of~$\Fan$.

\begin{corollary}
Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
\end{corollary}

@@

In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}. 
All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.
We first describe these associahedra and their type cones as they are the prototypes of our constructions.

\subsection{Classical associahedra}

We quickly recall the combinatorics and the geometric construction of~\cite{ShniderSternberg, Loday} for the associahedron~$\Asso[n]$.
The face lattice of~$\Asso[n]$ is the reverse inclusion lattice of dissections (\ie pairwise non-crossing subsets of diagonals) of a convex~$(n+3)$-gon.
In particular, its vertices correspond to triangulations of the $(n+3)$-gon and its facets correspond to internal diagonals of the $(n+3)$-gon.
Equivalently, its vertices correspond to rooted binary trees with $(n+1)$ internal nodes, and its facets correspond to proper intervals of~$[n+1]$ (\ie intervals distinct from~$\varnothing$ and~$[n+1]$).
These bijections become clear when the convex $(n+3)$-gon is drawn with its vertices on a concave curve labeled by~$0, \dots, n+2$.
The following statement provides three equivalent geometric constructions of~$\Asso[n]$.

\begin{proposition}
The associahedron~$\Asso[n]$ can be described equivalently as:
\begin{itemize}
\item the convex hull of the points~$L(T) \in \R^{n+1}$ for all rooted binary trees~$T$ with~$n+1$ internal nodes, where the $i$th coordinate of~$L(T)$ is the product of the number of leaves in the left subtree by the number of leaves in the right subtree of the $i$th node of~$T$ in inorder~\cite{Loday},
\item the intersection of the hyperplane~$\bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = \binom{n+2}{2}}$ with the halfspaces $\bigset{\b{x} \in \R^{n+1}}{\sum_{i \le \ell \le j} x_\ell \ge \binom{j-i+2}{2}}$ for all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{ShniderSternberg},
\item the Minkowski sum of the faces~$\simplex_{[i,j]}$ of the standard $n$-dimensional simplex~$\simplex$ corresponding to all proper intervals~$[i,j]$ of~$[n+1]$,~\cite{Postnikov}.
\end{itemize}
\end{proposition}

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ leaves in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.

\begin{proposition}
In the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$, 
\begin{itemize}
\item the normal vector of the facet corresponding to an internal diagonal~$(a,b)$ of the $(n+3)$-gon is the vector~$\gvector{a,b} \eqdef \pi\big( \sum_{a < \ell < b} \b{e}_\ell \big) = (n+1) \sum_{a < \ell < b} \b{e}_\ell - (j-i+1) \sum_{1 \le \ell \le n+1} \b{e}_\ell$.
\item the normal cone of the vertex corresponding to a rooted binary tree~$T$ is the incidence cone~$\bigset{\b{x} \in \HH}{x_i \le x_j \text{ for all edges $i \to j$ in $T$}}$.
\end{itemize}
\end{proposition}

Let us also recall the linear dependencies in this fan and observe that it has the unique exchange property.
From now on, we use the convention that~$\gvector{a,b} = 0$ when~$(a,b)$ is a boundary edge of the $(n+3)$-gon.

\begin{proposition}
\label{prop:exchangeablePairsAsso}
%Consider two exchangeable proper intervals~$[i,j]$ and~$[\ell,k]$ of~$[n+1]$, corresponding to two crossing diagonals~$(i-1,j+1)$ and~$(k-1,\ell+1)$ of the $(n+3)$-gon with~$0 \le i-1 < k-1 < j+1 < \ell+1 \le n+2$.
Consider two crossing diagonals~$(a,b)$ and~$(a',b')$, and any two triangulations~$T, T'$ such that~$T \ssm \{(a,b)\} = T' \ssm \{(a',b')\}$.
Then both triangulations~$T$ and~$T'$ contain the square $aa'bb'$, and the linear dependence between the $\b{g}$-vectors of~$T \cup T'$ is given by
\[
\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
\]
In particular, the fan~$\gvectorFan[n]$ has the unique exchange property.
\end{proposition}

From these linear dependencies, we obtain that the type cone of the fan~$\gvectorFan[n]$.

\begin{corollary}
Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
\[
\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
\]
\end{corollary}

We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.

\begin{proposition}
\label{prop:extremalExchangeablePairsAsso}
Two internal diagonals~$(a,b)$ and~$(a',b')$ of the~$(n+3)$-gon form an extremal exchangeable pair for the fan~$\gvectorFan[n]$ if and only if~$a = a'+1$ and~$b = b'+1$, or the opposite.
\end{proposition}

\begin{proof}
Let~$(\b{f}_{(a,b)})_{0 \le a < b \le n+2}$ be the canonical basis of~$\R^{\binom{n+3}{2}}$.
Consider two crossing internal diagonals~$(a,b)$ and~$(a',b')$ with~$0 \le a < a' < b < b' \le n+2$.
By \cref{prop:exchangeablePairsAsso}, the linear dependence between the corresponding $\b{g}$-vectors is given by
\[
\gvector{a,b} + \gvector{a',b'} = \gvector{a,b'} + \gvector{a',b}.
\]
Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[n])$ is
\[
\b{n}(a,b,a',b') \eqdef \b{f}_{(a,b)} + \b{f}_{(a',b')} - \b{f}_{(a,b')} - \b{f}_{(a',b)}.
\]
Denoting
\[
\b{m}(c,d) \eqdef \b{n}(c,d-1,c+1,d) = \b{f}_{(c,d-1)} + \b{f}_{(c+1,d)} - \b{f}_{(c,d)} - \b{f}_{(c+1,d-1)},
\]
we obtain that
\[
\b{n}(a,b,a',b') = \sum_{\substack{c \in {[a,a'[} \\ d \in {]b,b']}}} \b{m}(c,d).
\]
Indeed, on the right hand side, the basis vector~$\b{f}_{(c,d)}$ appears with a positive sign in~$\b{m}(c,d+1)$ for~$(c,d) \in {[a,a'[} \times {[b,b'[}$ and in~$\b{m}(c-1,d)$ for~$(c,d) \in {]a,a']} \times {]b,b']}$, and with a negative sign in~$\b{m}(c,d)$ for~$(c,d) \in {[a,a'[} \times {]b,b']}$ and in~$\b{m}(c-1,d+1)$ for~$(c,d) \in {]a,a']} \times {[b,b'[}$.
Therefore, these contributions all vanish except when~$(c,d)$ is one of the diagonals~$(a,b)$, $(a',b')$, $(a,b')$ or~$(a',b)$.
This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of diagonals~$(a,b)$ and~$(a',b')$ of the~$(n+3)$-gon such that~$a = a'+1$ and~$b = b'+1$ or the opposite.

Conversely, since~$\gvectorFan[n]$ has dimension~$n$ and~$n(n+3)/2$ rays (corresponding to the internal diagonals of the $(n+3)$-gon), we know from \cref{rem:dimTypeCone} that there are at least~$n(n+1)/2$ extremal exchangeable pairs. We thus conclude that all exchangeable pairs of diagonals~$\{(a,b-1), (a+1,b)\}$ for~$1 \le a < b-2 \le n$ are extremal.
\end{proof}

The following statement follows from the end of the previous proof.

\begin{corollary}
\label{coro:simplicialTypeConeAsso}
The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
\end{corollary}

Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeAsso} and \cref{prop:extremalExchangeablePairsAsso}, we derive the following description of all polytopal realizations of the fan~$\gvectorFan[n]$, thus recovering all associahedra of~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}.
We note that the arguments used in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} were quite different from the present approach.

\begin{corollary}[{\cite[Sect.~3.2]{ArkaniHamedBaiHeYan}}]
For~$n \in \N$, define~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$ and~$Y(n) \eqdef \set{(a,b)}{0 \le a < b-2 \le n}$.
Then for any~$\b{\ell} \in \R_{>0}^{Y(n)}$, the polytope
\[
R_\b{\ell}(n) \eqdef \set{\b{z} \in \R^{X(n)}}{\begin{array}{l} \b{z} \ge 0, \quad \b{z}_{(0,n+2)} = 0 \quad\text{and}\quad \b{z}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{z}_{(a,b-1)} + \b{z}_{(a+1,b)} - \b{z}_{(a,b)} - \b{z}_{(a+1,b-1)} = \b{\ell}_{(a,b)} \text{ for all } (a,b) \in Y(n) \end{array}}
%\bigset{\b{z} \in \R^{X(n)}}{\b{z} \ge 0, \; \b{z}_{1,n+1} = 0 \text{ and } \b{z}_{i,j} + \b{z}_{i+1,j+1} - \b{z}_{i,j+1} - \b{z}_{i+1,j} = \b{\ell}_{i,j} \text{ for } (i,j) \in X(n-1)}
\]
is an $n$-dimensional associahedron.
\end{corollary}

@@

A \defn{peak} (resp.~\defn{deep}) of a walk~$\omega$ is a substring of~$\omega$ of length zero which is on top (resp.~at the bottom of~$\omega$).
A walk~$\omega$ is \defn{straight} if it has no peak or deep (\ie if~$\omega$ or~$\omega^{-1}$ is a path in~$\quiver\blossom$), and \defn{bending} otherwise.
We denote by~$\peaks{\omega}$ (resp.~$\deeps{\omega}$) the multisets of vertices of peaks (resp.~deeps) of~$\omega$.

@@

\begin{corollary}
For any non-kissing finite gentle quiver~$\quiver$, the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ is given by
\[
\typeCone(\gvectorFan[\quiver]) = \set{\b{h} \in \R^{\walks}}{\begin{array}{l} \b{h}_\omega = 0 \text{ for any improper walk } \omega \\ \b{h}_\omega + \b{h}_{\omega'} > \b{h}_\mu + \b{h}_\nu \text{ for any exchangeable walks } \omega, \omega' \end{array}}.
\]
\end{corollary}

@@

Conversely, we know from \cref{rem:dimTypeCone} that there are at least~$|\properWalks|-|Q_0|$ extremal exchangeable pairs. Since this~$|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, we conclude that all exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for~$\sigma \in \strings$ are extremal.
\end{proof}

The following statement now follows from \cref{prop:bijectionStringsWalks,prop:extremalExchangeablePairsNKC}.

\begin{corollary}
\label{coro:simplicialTypeConeNKC}
For any gentle quiver~$\quiver$ with no self-kissing walk, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
\end{corollary}

Combining \cref{coro:simplicialTypeCone}, \cref{coro:simplicialTypeConeNKC} and \cref{prop:extremalExchangeablePairsNKC}, we derive the following description of all polytopal realizations of the non-kissing fan~$\gvectorFan[\quiver]$ of a quiver~$\quiver$ with no self-kissing~walk.

\begin{corollary}
For any gentle quiver~$\quiver$ with no self-kissing walk and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{corollary}

\begin{proof}
\cref{prop:extremalExchangeablePairsNKC} asserts that the type cone~$\typeCone(\gvectorFan[\quiver])$ has one facet for each string of~$\quiver$.
Since all strings are distinguishable by \cref{prop:noSelfKissing}, the number of facets of~$\typeCone(\gvectorFan[\quiver])$ is $|\strings| = |\distinguishableStrings| = |\properWalks| - |Q_0|$ by~\cref{prop:bijectionStringsWalks}, so that~$\typeCone(\gvectorFan[\quiver])$ is simplicial. We then conclude by a simple application of \cref{coro:simplicialTypeCone}.
\end{proof}

@@

\begin{remark}
\label{rem:meshARquiver}
Although not needed in the proof of \cref{prop:extremalExchangeablePairsNKC}, we note that the extremal exchangeable pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ and their linear dependencies~${\gvector{\cc{\sigma}} + \gvector{\hh{\sigma}} - \gvector{\hc{\sigma}} - \gvector{\ch{\sigma}}}$ precisely correspond to the meshes of the Auslander-Reiten quiver of~$\quiver$.
\end{remark}

@@

We are already missing a criterion for exchangeable pairs of walks. See \cite[Sect.~9]{BrustleDouvilleMousavandThomasYildirim}.
It seems that two exchangeable walks are always kissing along a single distinguishable string.
We need to prove that to see that the non-kissing fan has the unique exchange relation property (because for a pair of exchangeable walks, I can completely reconstruct the $\b{g}$-vector dependence of the flip if I know their distinguished substring).
Note however that
\begin{enumerate}
\item exchangeable pairs might kiss along additional non-distinguishable strings (example: just a loop),
\item non-exchangeable walks might kiss along a single distinguishable string (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
\item non-exchangeable walks might kiss along two or more distinguishable strings (example: see the cyclic triangle in~\cite{PaluPilaudPlamondon-nonkissing}).
\end{enumerate}

@@

\para{Nested complex}
%
Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
The tubes which are neither empty nor maximal are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.

@@

We start with the case of the path on~$n+1$ vertices.
Recall that the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

\begin{proposition}
\label{prop:extremalExchangeablePairsA}
%The extremal exchangeable pairs for the nested fan of the path are precisely the pairs of intervals~$\{[i,j], [i+1,j+1]\}$ for~$1 \le i \le j \le n-1$.
Two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ form an extremal exchangeable pair for the nested fan of the path if and only if~$i = i'+1$ and~$j = j'+1$, or the opposite.
\end{proposition}

\begin{proof}
Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ be the canonical basis of~$\R^{\binom{n+1}{2}}$.
Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~${i < i' \le j+1 < j'+1}$.
By \cref{prop:exchangeablePairsGA}\,(iii), the linear dependence between the corresponding $\b{g}$-vectors is given by
\[
\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}.
\]
Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\graphG])$ is
\[
\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}.
\]
Denoting
\[
\b{m}(k,\ell) \eqdef \b{n}(k,\ell-1,k+1,\ell) = \b{f}_{[k, \ell-1]} + \b{f}_{[k+1, \ell]} - \b{f}_{[k, \ell]} - \b{f}_{[k+1, \ell-1]},
\]
we obtain that
\[
\b{n}(i,j,i',j') = \sum_{\substack{k \in {[i,i'[} \\ \ell \in {]j,j']}}} \b{m}(k,\ell).
\]
Indeed, on the right hand side, the basis vector~$\b{f}_{[k,\ell]}$ appears with a positive sign in~$\b{m}(k,{\ell+1})$ for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and in~$\b{m}(k-1, \ell)$ for~$(k,\ell) \in {]i,i']} \times {]j,j']}$, and with a negative sign in~$\b{m}(k,\ell)$ for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and in~$\b{m}(k-1,\ell+1)$ for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
%For any~$i \le k < i'$ and~$j < \ell \le j'$, the exchange relation between the tubes~$[k, \ell-1]$ and~$[k+1, \ell]$ is given by
%\begin{equation}
%\label{eq:exch2}
%\tag{$\mathrm{ER}_k^\ell$}
%\gvector{[k, \ell-1]} + \gvector{[k+1, \ell]} = \gvector{[k, \ell]} + \gvector{[k+1, \ell-1]}.
%\end{equation}
%Summing the exchange relations~\eqref{eq:exch2} over all pairs~$(k,\ell) \in {[i,i'[} \times {]j,j']}$, we obtain after simplifications the exchange relation~\eqref{eq:exch1}.
%Indeed, the $\b{g}$-vector of each tube~$[k, \ell]$ appears on the left hand sides of the exchange relations~($\mathrm{ER}_k^{\ell+1}$) for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and ($\mathrm{ER}_{k-1}^\ell$) for~$(k,\ell) \in {]i,i']} \times {]j,j']}$ and on the right hand sides of the exchange relations~($\mathrm{ER}_k^\ell$) for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and~($\mathrm{ER}_{k-1}^{\ell+1}$) for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
%Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n+1]$ such that~$i = i'+1$ and~$j = j'+1$.
